\chapter{BGG category $\mathcal{O}$ and Lie algebra (co)homology}


\section{BGG category $\mathcal{O}$}

This chapter contains the description of Bernstein-Bernstein-Gelfand category $\mathcal{O}$ and a small recapitulation of Enright-Shelton equivalences which will be needed later.


\subsection{Generalized Verma modules and the Shapovalov form}


For any $\lambda\in\lie{h}^*$ we denote by $\C_\lambda$ the one dimensional representation of $\lie{h}$ on with character $\lambda$. We extend the action to $\lie{b}^- := \lie{n}^-\oplus\lie{h}$ by letting $\lie{n}^-$ act trivially. The \emph{Verma module} $N(\lambda)$ is then defined as $N(\lambda) := \lie{U(g)}\otimes_{\lie{U(b^-)}} \C_\lambda$. We will denote its highest weight vector by $v_\lambda$.

Let $\lambda$ be a $\Delta_c^+$ dominant and integral weight and denote by $F(\lambda)$ the finite dimensional irreducible $\lie{k}$-module.  We extend any irreducible representation of $K_\mathbb{C}$ to $P$ and to $\overline{P}$ by letting $\lie{p}_+$ and $\lie{p}_-$ act trivially. The \emph{generalized Verma module} $M(\lambda)$ is defined as $M(\lambda) = \lie{U}(\lie{g}) \otimes_{\lie{U}(\oppar)} F(\lambda)$. It is well known and easy to prove that $M(\lambda)$ contains a maximal nontrivial submodule $J(\lambda)$ and we denote by $L(\lambda)$ the corresponding irreducible quotient of $M(\lambda)$. Since the nilradical $\lie{p}_-$ of $\oppar$ is abelian and acts trivially on $F(\lambda)$, we have that $M(\lambda) \simeq S(\lie{p}_+)\otimes F(\lambda)$ as $K_\C$ representations, where $S(\lie{p}_+)$ is the symmetric algebra  over the Lie algebra $\lie{p}_+$.
%The canonical $\overline{P}$-invariant filtration of $M(\lambda) = \bigcup_{k\geq 0} M^k(\lambda)$ has filtration components $M^k(\lambda)= \{\epsilon^{i_1}\cdots\epsilon^{i_j}\otimes v\, | v \in F(\lambda), j \leq k \}$.
In the case of $M(\lambda)$, the geometric weight corresponds to the polynomial degree shifted by the weight of $F(\lambda)$.% and the canonical $\overline{P}$-invariant filtration is the same as the filtration induced by the geometric weight.

Let $\sigma$ be involutive antiautomorphism on $\lie{U(g)}$ such that it's restriction on the real form $\lie{g}_0$ is $-\id$. With our choice of Cartan subalgebra $\lie{h}$ we have that $\sigma: X_\beta \mapsto X_{-\beta}$ for $X_\beta \in \lie{g}_\beta$ and $\sigma: h_\alpha \mapsto h_\alpha$ for $h_\alpha \in \lie{h}$.

Let $P: \lie{U(g)} \to \lie{U(h)}$ be the projection defined by the splitting \[\lie{U(g)} = \lie{U(h)}\oplus \left( \lie{n_-U(g)} + \lie{U(g)n_+} \right)\]

\begin{definition}
  The \emph{universal Shapovalov form} on $\lie{U(g)}$ is defined as \[\langle u_1 , u_2 \rangle = P(\sigma(u_1)u_2).\] It is a bilinear form on $\lie{U(g)}$ with values in $\lie{U(h)} = S(\lie{h})$.

  For $\lambda\in\lie{h}^*$ we define the \emph{Shapovalov form on the Verma module} $N(\lambda)$ by \[\langle u_1 v_\lambda , u_2 v_\lambda \rangle = P(\sigma(u)v)(\lambda).\]
\end{definition}

It is easy to see that $\langle u\cdot v,v' \rangle = \langle v,\sigma(u)\cdot v' \rangle$ for all $v,v'\in M_\lambda$ and for all $u\in \lie{U(g)}$. Forms with such a property are called \emph{contravariant forms}.

The following proposition and its proof can be found e.g. in \cite{humphreys}.

\begin{proposition}
Contravariant forms have the following properties:
\begin{enumerate}
 \item If the $\lie{U(g)}$-module $M$ has a contravariant form $(v,v')_M$, then the weight spaces are orthogonal. I.e. $( M_\mu,M_\nu)=0$ whenever $\mu\neq\nu$ in $\lie{h}^*$.
 \item Suppose $M = \lie{U(g)} \cdot v$ is a highest weight module generated by a maximal vector $v$ of weight $\lambda$. If $M$ has a nonzero contravariant form, then the form is uniquely determined up to a scalar multiple by the (nonzero!) value $( v, v)_M$.
 \item  If $\lie{U(g)}$-modules $M_1, M_2$ have contravariant forms $(v, v')_{M_1}$ and $(w,w')_{M_2}$ , then $M := M_1\otimes M_2$ also has a contravariant form, given by \[(v\otimes w, v'\otimes w')_M := (v, v')_{M_1} (w,w')_{M_2}.\] In case both of the forms are nondegenerate, so is the product form.
 \item If $M$ has a contravariant form and $N$ is a submodule, the orthogonal complement $N^\perp := \{v\in M | (v, v')_M = 0 \text{ for all } v' \in N \}$ is also a submodule.
\end{enumerate}
\end{proposition}
\begin{proof}
\begin{enumerate}
 \item We use the fact that $\sigma(h) = h$ for $h\in\lie{h}$. Let $v$ be a vector of weight $\mu$ and let $v'$ be a vector of weight $\nu$. The for any $h\in\lie{h}$ we have
 \[
  \mu(h)(v,v')_M = (h\cdot v,v')_M = (v,\sigma(h)\cdot v')_M = (v,h\cdot v')_M = \nu(h)(v,v')_M.
 \]
 Since $v,v'$ were arbitrary we must have $(v,v')=0$ for $\mu\neq \nu$.
 \item In view of the already proven point it suffices to look at values of the form on a weight
space $M_\mu$. Typical vectors $v, v' \in M_\mu$ can be written as $u\cdot v, u'\cdot v$ for suitable $u, u'\in\lie{U(n)}$. Note that since $u$ takes $M_\lambda$ into $M_\mu$, the element $\sigma(u) \in \lie{U(n^-)}$ takes $M_\mu$ into $M_\lambda$ (which is spanned by $v$). Then $(v, v')_M = (u\cdot v, u'\cdot v)_M = (v, \sigma(u)u'\cdot v)_M$, which is a scalar multiple of $(v, v)_M$ depending just on the action of $\lie{U(g)}$ and not on the choice of the form.

The remaining points are elementary.
\end{enumerate}
\end{proof}

Important consequence of this is the following lemma.
\begin{lemma}
The maximal submodule of $N(\lambda)$ is the radical of the Shapovalov form.
\end{lemma}
\begin{proof}
Let $v\in J(\lambda)$  be arbitrary. Then $\langle v, v_\lambda \rangle = 0$ since clearly $v$ and $v_\lambda$ have different weights. Since $J(\lambda)^\perp$ is a submodule of $N(\lambda)$ containing the generating vector $v_\lambda$ the statement follows.
\end{proof}

The generalized Verma module $M(\lambda)$ is a quotient of the Verma module $N(\lambda)$. Hence the simple quotient $L(\lambda)$ of $M(\lambda)$ is also a quotient of $N(\lambda)$ by its maximal submodule. We get induced contravariant forms on $L(\lambda)$ and $M(\lambda)$  which we also call Shapovalov forms and we denote them by a same symbol.

\subsection{Category $\mathcal{O}$ and translation functors}

We present a short overview of translation functors as is presented in \cite{humphreys}. Since we deal with integral weights only, we omit all the notations that concerns nonintegral weights.

\begin{definition}
  Let $\lambda, \mu \in \weights$ be such that $\nu = \mu - \lambda \in \weights^+$ and consider a finite dimensional representation $F(\nu)$ of highest weight $\nu$. Then the translation functor $T_\lambda^\mu: \mathcal{O}_\mu \to \mathcal{O}_\lambda$ is defined by
  \[
   T_\lambda^\mu M := \proj(F(\nu)\otimes M),
  \]
  where $\proj$ is the projection from $\mathcal{O}$ to $\mathcal{O}_\mu$.
\end{definition}

The vector space $\lie{h}^*$ decomposes into so called facets for the affine Weyl group action according to decompositions of the set of positive roots $\roots^+$ as follows. The facet $F$ corresponding to $\roots^+ = \roots^+_- \cup \roots^+_0 \cup \roots^+_+$ is defined as the set of those $\lambda \in \lie{h}$ such that
\[
  \begin{cases}
   (\lambda + \rho, \alpha) < 0, & \forall \alpha \in \roots^+_- \\
   (\lambda + \rho, \alpha) = 0, & \forall \alpha \in \roots^+_0 \\
   (\lambda + \rho, \alpha) > 0, & \forall \alpha \in \roots^+_+.
  \end{cases}
\]

\begin{theorem}[Theorem 7.?? of \cite{humphreys}]\label{thm:translation}
 If two weights $\mu$ and $\lambda$ lie in the same facet, then the translation functors $T_\lambda^\mu$ and $T_\mu^\lambda$ implement an equivalence of categories between $\mathcal{O}_\mu$ and $\mathcal{O}_\lambda$.
\end{theorem}


\subsection{Equivalences of Enright and Shelton}

\section{Harish-Chandra modules and their globalizations}


\noindent Fix a maximal compact subgroup $K_{0}$ of $G_{0}$. Suppose we have
a linear action of $K_{0}$ on a complex vector space $M$. A vector $m\in M$
is called $K_{0}-$\emph{finite} if the span of the $K_{0}-$orbit of $m$ is
finite-dimensional and if the action of $K_{0}$ in this subspace is
continuous. The linear action of $K_{0}$ in $M$ is called $K_{0}-$\emph{%
finite }when every vector is $K_{0}-$finite. By definition, \emph{a
Harish-Chandra module} for $G_{0}$ is a finite length $\mathfrak{g}-$module $%
M$ equipped with a compatible, $K_{0}-$finite, linear action. One knows that
an irreducible $K_{0}-$module has finite multiplicity in a Harish-Chandra
module. For our purposes, it will also be useful to refer to a category of
\emph{good }$K_{0}-$modules. A \emph{good }$K_{0}-$module will mean a
locally finite module such that each irreducible $K_{0}-$module has finite
multiplicity therein.

\smallskip

\noindent A representation of $G_{0}$ in a complete locally convex
topological vector space $V$ is called \emph{admissible} if $V$ has finite
length (with respect to closed invariant subspaces) and if each irreducible $%
K_{0}-$module has finite multiplicity in $V$. When $V$ is admissible, then
each $K_{0}-$finite vector in $V$ is differentiable and the subspace of $%
K_{0}-$finite vectors is a Harish-Chandra module. The representation is
called \emph{smooth} if every vector in $V$ is differentiable. In this case,
$V$ is a $\mathfrak{g}-$module. For example, one knows that an admissible
representation in a Banach space is smooth if and only if the representation
is finite-dimensional.

\smallskip \smallskip

\noindent Given a Harish-Chandra module $M$, \emph{a globalization} $M_{%
\text{glob}}$ \emph{of }$M$ is an admissible representation of $G_{0}$ whose
underlying $(\mathfrak{g},K_{0})-$module of $K_{0}-$finite vectors is
isomorphic to $M$. By now, four canonical globalizations of Harish-Chandra
modules are known to exist. These are: the smooth globalization of Casselman
and Wallach \cite{C}, its dual (called: the distribution globalization),
Schmid's minimal globalization \cite{S} and its dual (the maximal
globalization). All four globalizations are smooth and functorial. In this
article we focus on the minimal and maximal globalizations of Schmid.

\smallskip \smallskip

\noindent The \emph{minimal globalization }$M_{\text{min}}$ of a
Harish-Chandra module $M$ is uniquely characterized by the property that any
$(\mathfrak{g},K_{0})-$equivariant linear of $M$ onto the $K_{0}-$finite
vectors of an admissible representation $V$ lifts to a unique, continuous $%
G_{0}-$equivariant linear map of $M_{\text{min}}$ into $V$. In particular, $%
M_{\text{min}}$ embeds $G_{0}-$equivariantly and continuously into any
globalization of $M$. The construction of the minimal globalization shows
that it's realized on a \emph{DNF space}. This means that its continuous
dual, in the strong topology, is a nuclear Frech\'{e}t space. One knows that
$M_{\text{min}}$ consists of analytic vectors and that it surjects onto the
analytic vectors in a Banach space globalization. Like each of the canonical
globalizations, the minimal globalization is functorially exact. In
particular, a closed $G_{0}-$invariant subspace of a minimal globalization
is the minimal globalization of its underlying Harish-Chandra module and a
continuous $G_{0}-$equivariant linear map between minimal globalizations has
closed range.

\smallskip

\noindent To characterize the maximal globalization, we introduce the $%
K_{0}- $finite dual on the category of Harish-Chandra modules. In
particular, let $M $ be a Harish-Chandra module. Then the algebraic dual $%
M^{\ast }$ of $M$ is a $\mathfrak{g}-$module and a $K_{0}-$module, but in
general not $K_{0}-$finite. We define $M^{\vee }$, \emph{the} $K_{0}-$\emph{%
finite (or Harish-Chandra) dual to} $M$, to be the subspace of $K_{0}-$%
finite vectors in $M^{\ast }$. Thus $M^{\vee }$ is a Harish-Chandra module.
In fact, the functor $M\mapsto M^{\vee }$ is exact on the category of good $%
K_{0}-$modules. We also have the formula
\begin{equation*}
\left( M^{\vee }\right) ^{\vee }\cong M\text{.}
\end{equation*}%
The maximal globalization $M_{\text{max}}$ of $M$ can be defined by the
equation%
\begin{equation*}
M_{\text{max}}=\left( \left( M^{\vee }\right) _{\text{min}}\right) ^{\prime }
\end{equation*}%
where the last prime denotes the continuous dual equipped with the strong
topology. In particular, $M_{\text{max}}$ is a globalization of $M$. Observe
that the maximal globalization is an exact functor, since all functors used
in the definition are exact. Because of the minimal property of $M_{\text{min%
}}$, it follows that any globalization of $M$ embeds continuously and
equivariantly into $M_{\text{max}}$. Note that the continuous dual of a
maximal globalization is the minimal globalization of the dual
Harish-Chandra module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The problem is that $L(\lambda)$ is not a $P$-representation.  This is not surprising because the generalized Verma module $M(\lambda)$ was induced from a $\overline{P}$-representation. Let $L(\lambda)=\bigoplus_{\mu\in \widehat{K}_\C} L_\mu$ be the decomposition of $L(\lambda)$ into $K_\C$-types. Each $L_\mu$ is contained in some $S^k(\lie{p}_+,F(\lambda))$ modulo the maximal submodule of $M(\lambda)$ and the algebra $\lie{p}_+$ acts  as a multiplication by a variable, while $\lie{p}_-$ acts basically as a differentiation. To formalize this write $L(\lambda) = \bigoplus_{\mu\in\widehat{K_\C}, k\in\mathbb{N}} L_{\mu,k}$ where $L_{\mu,k}$ is the $K_\C$-type contained in $S^k(\lie{p}_+,F(\lambda))$ and note that $\lie{p}_+ (L_{\mu,k}) \subset L_{\mu,k+1}$.

The \emph{formal globalization} of $L(\lambda)$ is defined as   $\overline{L(\lambda)}=\prod_{\mu\in \widehat{K}_\C} L_\mu$ (product of topological vector spaces). (See e.g \cite{vogan_jr._unitary_2008}.) Since each $K_\C$-type is finite-dimensional and each $S^k(\lie{p}_+,F(\lambda))$ contains only finitely many irreducible $K_\C$-representations, we can write it as
\[\overline{L(\lambda)} = \prod_{k\in\mathbb{N}} L_k,\] %TODO predelat do lemmatu s dukazem?
where $L_k = \bigoplus_{\mu\in\widehat{K_c}} L_{\mu,k}$ is a finite sum. The action of $\lie{p}_+$ works as a right shift: $\lie{p}_+(L_k)\subset L_{k+1}$. The $(\lie{g},K)$-module $L(\lambda)$ can be realized as a space of polynomials with values in a finite dimensional $K$-representation $F_\lambda$ and it's formal completion can be thought of as a space of formal power series with values in $F_\lambda$. %TODO posledni vetu predelat do lematu s dukazem?

Now it is easy to see that the formal globalization  is a representation of $P$. The action of $\lie{p}_+$ on $\overline{L(\lambda)}$ integrates without any problems. Let $X$ be an arbitrary element of $\lie{p}_+.$ The exponential $u:=\exp(tX)v$ is defined for $v\in\overline{L(\lambda)}$ as usual by $\sum_{i=0}^\infty \frac{t^i}{i!} X^iv$. This is well defined for $v$ if and only if each component $u_\mu$ is well defined. If $u_\mu$ is contained in some $S^k(\lie{p}_+,F(\lambda))$, then it is a sum of at most $k$ elements of lower or equal geometric weight.



Let's consider a simple Lie group $G$ with a parabolic subgroup $P$, $\mathfrak{p} = \mathfrak{l}\oplus\mathfrak{n}$ and let $L$ be the Levi part of $P$ and $E\in \mathfrak{l}$ the grading element. Any simple highest weight representation  $\mathbb{V}$ of the pair $(\mathfrak{g},L)$ decomposes into eigenspaces of $\mathrm{ad}(E)$ and the same is true also for $\Lambda^k\mathfrak{n}\otimes\mathbb{V}$, $k\in \mathbb{N}$.

The formal completion of $\mathbb{V}$ is denoted by $\overline{\mathbb{V}}$ and can be defined e.g. as $\overline{\mathbb{V}} = (\mathbb{V}^\vee)^*$, where $\mathbb{V}^\vee$ is the $L$-finite submodule of the dual of $V$ (i.e. a nontwisted duality  in category $\mathcal{O}$). As $L$-representations we have

$$
\mathbb{V} = \bigoplus_i \mathbb{V}_i, \qquad \overline{\mathbb{V}}  = \prod_i \mathbb{V}_i
$$

and $\mathbb{V}$ is a $(\mathfrak{g},L)$-submodule of $\overline{\mathbb{V}}$.

\begin{proposition}
 Suppose that the Lie algebra homology and cohomology differentials are disjoint for $\mathbb{V}$, i.e. $\ker \delta \cap \im \delta^* = 0$ and $\ker \delta^* \cap \im \delta = 0$. We state that differentials are still disjoint for the formal completion of $\mathbb{V}$. Moreover, if the homology (or equivalently cohomology) of $\mathbb{V}$ is finite-dimensional, then it is equal to the cohomology of the formal completion.
\end{proposition}

\begin{proof}

Elements of the formal completion (of an infinite-dimensional module) $\mathbb{W}$ can be written as infinite tuples of elements of $\mathbb{W}$
$$
u\in\overline{\mathbb{W}} \leftrightarrow u = (u_i)_{i\in I},
$$
where the index set $I$ runs over all eigenvalues of the action of $E$ on $\mathbb{W}$. And a formal completion of $ \Lambda^k \mathfrak{n} \otimes \mathbb{V}$ is  $\Lambda^k \mathfrak{n}  \otimes \overline{\mathbb{V}}$.

For a contradiction, suppose that there is nonzero $u$ in $\ker \delta \cap \im \delta^*$. Without a loss of generality, we can consider $u$ to be an element of the $k$-th chain space. Let's denote this $k$-th chain space  $\Lambda^k\otimes \mathbb{V}$ by $\mathbb{W}$ Since $u$ is nonzero, there must exists $i$ such that $u_i\neq 0$. Both differentials are natural, which means that they commute with restriction from $\overline{\mathbb{W}}$ to $\mathbb{W}$. They are moreover $L$-invariant, which in particular means that they commute with the action of the grading element, which means that they act component-wise on $(u_i)_{i \in I}$. It follows that if we take $\widetilde{u}= (\widetilde{u_j})\in \mathbb{W} \subseteq \overline{\mathbb{W}}$ to be zero  for $j\neq i$ and $\widetilde{u_i} = u_i$, then we have $\delta \widetilde{u} = 0$.  Since $u\in \im \delta^*$, there must exists a $v\in\overline{\mathbb{W}}$ such that $\delta^* v = u$ and we can define in the same way as before a $\widetilde{v}\in\mathbb{W}$
such that $\delta^* \widetilde{v} = \widetilde{u}$. Thus we see that there is a non-zero element in $\ker \delta \cap \im \delta^*\cap \Lambda^k\otimes \mathbb{W}$. This is a contradiction with the assumption that $\delta$ and $\delta^*$ are disjoint for $\mathbb{V}$.


Basically, the same argument proves that the cohomology must stay the same if it is finite-dimensional. From the Hodge theory (which is implied by the disjointness) we know that any element of the cohomology group can be uniquely represented by an alement in $\ker (\delta + \delta^*)$. Let $D=\delta + \delta^*$ and suppose for a contradiction that there is a nonzero element $(u_i)$ in $\ker D \setminus \ker D_{|\mathbb{W}}$, where $\mathbb{W}$ is the $k$-th chain space of $\mathbb{V}$. Pick $i_0$ such that $u_{i_0} \neq 0$ and $i_0$ is bigger than any eigenvalue of $E$ on $\ker D_{|\mathbb{W}}$.\footnote{This is well defined because of the finite-dimensionality of $\ker D_{|\mathbb{W}}$.} Since $D$ is again $L$ invariant we proceed as before and construct $\widetilde{u}\in\mathbb{W}\cap\ker D$. The choice of $i_0$ now leads to the desired contradiction.

\end{proof}

Hodge theory for nilpotent (co)homoloy was invented by Kostant in \cite{kostant_lie_1961}.

\section{Cohomology and homology of Lie algebras}

In this section we denote by $\lie{m}$ an arbitrary Lie algebra and by $\rep{V}$ its representation. We will denote the action of $\lie{m}$ on $\rep{V}$ by a dot.

The chain spaces of \emph{Lie algebra homology} $C_k(m,\rep{V})$ of the algebra $\lie{m}$ with values in $\rep{V}$ are defined as $\Lambda^k\lie{m}\otimes\rep{V}$. The Lie algebra \emph{homology differential} \[\lhd_\lie{m} : C_{k+1}(\lie{m},\rep{V}) \to C_k(\lie{m},\rep{V})\] is defined by the following formula
\begin{multline*}
\lhd_\lie{m} (Z_0\wedge\cdots Z_k\otimes v) = \sum_{i=0}^k (-1)^{i+1} Z_0\wedge\cdots\wedge\widehat{Z_i}\wedge\cdots\wedge Z_k\otimes Z_i\cdot v\,  + \\
				      +\sum_{i<j} (-1)^{i+j} [Z_i,Z_j]\wedge Z_0\wedge\cdots\wedge\widehat{Z_i}\wedge\cdots\wedge\widehat{Z_j}\wedge\cdots\wedge Z_k\otimes v,
\end{multline*}
where $Z_i\in\lie{m}$ for $i=0,\ldots,k$. If the algebra $\lie{m}$ is abelian, then the second term in the sum is zero.

The cochain spaces of \emph{Lie algebra cohomology} $C^k(\lie{m},\rep{V})$ are defined as $\Hom(\Lambda^k \lie{m},\rep{V})$. The Lie algebra \emph{cohomology differential} \[\lcd_\lie{m} :  C^k(\lie{m},\rep{V}) \to C^{k+1}(\lie{m},\rep{V})\] is defined as
\begin{multline*}
 (\lcd_\lie{m} \phi)(X_0,\ldots, X_n) = \sum_{i=0}^n (-1)^i X_i \cdot \phi(X_0,\ldots,\widehat{X_i},\ldots, X_n)\, + \\
				+\sum_{i<j} (-1)^{i+j} \phi([X_i,X_j],X_0,\ldots,\widehat{X_i},\ldots,\widehat{X_j},\ldots,X_n),
\end{multline*}
where $X_0,\ldots, X_n \in \lie{m}$ and $\phi:\Lambda^k \lie{m} \to \rep{V}$. Again, we can forget the second term if the algebra $\lie{m}$ is commutative.

There is a natural identification of $C_k(\lie{m}^*,\rep{V})$ and $C^k(\lie{m},\rep{V})$ coming from the natural isomorphism $\Lambda^k \lie{m}^* \otimes \rep{V} \simeq \Hom(\lie{m},\rep{V})$.

We can identify $C^k(\lie{p}_-,\rep{V})=\Hom (\Lambda^k\lie{p}_-,\rep{V})$ with $\Lambda^k {\lie{p}_-}^*\otimes\rep{V}$. Since the Killing form induces an isomorphism ${\lie{p}_-}^* \simeq \lie{p}_+$, we can consider the Lie algebra cohomology differential $\lcd$ as an operator on the chain spaces of Lie algebra homology $\lcd: \Lambda^k {\lie{p}_-}^* \otimes V \to \Lambda^{k+1}{\lie{p}_-}^*\otimes V$. After these identifications we get the formula
\[
 \lcd  (Z_1\wedge\cdots\wedge Z_k\otimes v) = \sum_{i=1}^{2p} \epsilon^i \wedge Z_1\wedge\cdots\wedge Z_k\otimes e_i\cdot v.
\] The Lie algebra cohomology differential is $\overline{P}$-equivariant. In particular, both $\lcd$ and $\lhd$ are $K_\C$-equivariant and consequently they preserve the geometric weight.

The Kostant Laplacian is defined on each $C_k(\lie{p}_+,\rep{V})$ as $\lap = \lhd \lcd + \lcd \lhd$. It was proven in \cite{kostant_lie_1961} that for a finite-dimensional $\lie{g}$-representation $\rep{V}$ there is a positive definite scalar product on $C_\bullet(\lie{p}_+,\rep{V})$ with respect to which are $\lcd$ and $\lhd$ adjoint. It follows that there is a direct sum \emph{Hodge decomposition} of $K_\C$-modules $C_\bullet(\lie{p}_+,\rep{V})=\im \lcd \oplus  \ker \lap \oplus \im \lhd$ and moreover $\ker \lhd = \ker \lap \oplus \im \lhd$ and $\ker \lcd = \ker \lap \oplus \im \lcd$. It follows that $H_\bullet(\lie{p}_+,\rep{V})\simeq \ker \lap \simeq H^\bullet(\lie{p}_-,\rep{V})$.

%\subsection{Invariant and coinvariant functors and their derivations}

\noindent \emph{The right standard resolution of }$\mathbb{C}$ is the
complex of free right $U(\mathfrak{n})-$modules given by
\begin{equation*}
\cdots \rightarrow \Lambda ^{p+1}\mathfrak{n}\otimes U(\mathfrak{n}%
)\rightarrow \Lambda ^{p}\mathfrak{n}\otimes U(\mathfrak{n})\rightarrow
\cdots \rightarrow \mathfrak{n}\otimes U(\mathfrak{n})\rightarrow U(%
\mathfrak{n})\rightarrow 0\text{.}
\end{equation*}%
Applying the functor
\begin{equation*}
-\otimes _{U(\mathfrak{n})}M\text{ }
\end{equation*}%
to the standard resolution we obtain a complex
\begin{equation*}
\cdots \rightarrow \Lambda ^{p+1}\mathfrak{n}\otimes M\rightarrow \Lambda
^{p}\mathfrak{n}\otimes M\rightarrow \cdots \rightarrow \mathfrak{n}\otimes
M\rightarrow M\rightarrow 0
\end{equation*}%
of left $\mathfrak{l}-$modules called \emph{the standard} $\mathfrak{n}-$%
\emph{homology complex}. Here $\mathfrak{l}$ acts via the tensor product of
the adjoint action on $\Lambda ^{p}\mathfrak{n}$ with the given action on $M$%
. Since $U(\mathfrak{g})$ is free as $U(\mathfrak{n})-$module, a routine
homological argument identifies the pth$-$homology of the standard complex
with the pth $\mathfrak{n}-$homology group
\begin{equation*}
H_{\text{p}}(\mathfrak{n},M).
\end{equation*}%
One knows that the induced $\mathfrak{l}-$action on the homology groups of
the standard complex is the correct one.

\smallskip

\noindent The \emph{zero} $\mathfrak{n}-$\emph{cohomology }of a $\mathfrak{g}%
-$module $M$ is the $\mathfrak{l}-$module
\begin{equation*}
H^{0}(\mathfrak{n},M)=\text{Hom}_{U(\mathfrak{n})}(\mathbb{C},M).
\end{equation*}%
This determines a left exact functor from the category of $\mathfrak{g}-$%
modules to the category of $\mathfrak{l}-$modules. By definition, \emph{the}
$\mathfrak{n}-$\emph{cohomology groups of} $M$ are the $\mathfrak{l}-$%
modules obtained as the corresponding derived functors. These $\mathfrak{l}-$%
modules can be calculated by applying the functor
\begin{equation*}
\text{Hom}_{U(\mathfrak{n})}(-,M)
\end{equation*}%
to the standard resolution of $\mathbb{C}$, this time by free left $U(%
\mathfrak{n})-$modules. In a natural way, one obtains a complex of $%
\mathfrak{l}-$modules and pth cohomology of this complex realizes the pth $%
\mathfrak{n}-$cohomology group

\begin{equation*}
H^{\text{p}}(\mathfrak{n},M).
\end{equation*}

\noindent Let $\mathfrak{n}^{\ast }$denote the $\mathfrak{l}-$module dual to
$\mathfrak{n}$. Then, using the standard complexes and the natural
isomorphism of $\mathfrak{l}-$modules
\begin{equation*}
\Lambda ^{p}\mathfrak{n}^{\ast }\otimes M\cong \text{Hom}(\Lambda ^{p}%
\mathfrak{n},M)
\end{equation*}%
one can deduce the following well known fact \cite[Section 2]{HS}:

\begin{proposition}
Suppose $M$ is a $\mathfrak{g-}$module. Let $\mathfrak{p}\subseteq \mathfrak{%
g}$ be a parabolic subalgebra with nilradical $\mathfrak{n}$ and Levi factor
$\mathfrak{l}$. \newline
(a) Let $M^{\ast }$ denote the $\mathfrak{g}-$module dual to $M.$ Then there
is a natural isomorphism
\begin{equation*}
H_{\text{p}}(\mathfrak{n},M^{\ast })\cong H^{\text{p}}(\mathfrak{n},M)^{\ast
}
\end{equation*}%
where $H^{\text{p}}(\mathfrak{n},M)^{\ast }$ denotes the $\mathfrak{l-}$%
module dual to $H^{\text{p}}(\mathfrak{n},M)$.\newline
(b) Let d denote the dimension of $\mathfrak{n}$. Then there is a natural
isomorphism
\begin{equation*}
H_{\text{p}}(\mathfrak{n},M)\cong H^{\text{d-p}}(\mathfrak{n},M)\otimes
\Lambda ^{\text{d}}\mathfrak{n}\newline
\end{equation*}
\end{proposition}



%\subsection{Real versus complex}

\begin{proposition}[Proposition 3.3.6 of \cite{cap_parabolic_2009}]
 Let $\lie{g}$ be a $|k|$-graded semisimple Lie algebra with complexification $\lie{g}^\C$ and let $\rep{V}$ be a complex representation of $\lie{g}$. Then the real cohomology spaces $H^*(\lie{g}_-,\rep{V})$ are 	naturally complex vector spaces and we have a natural isomorphism of $\lie{g}_0$-modules
 \[
  H_\R^*(\lie{g}_-,\rep{V}) \simeq H_\C^*(\lie{g}_-^\C,\rep{V}).
 \]

\end{proposition}


\subsection{Disjoint operators and Hodge decomposition}

Let $V$ be a topological vector space and let $\lcd$ and $\lhd$ be two linear operators on $V$ such that $\lcd^2 = \lhd^2 = 0$. Such operators are called \emph{disjoint} if
\begin{gather*}
 \lcd\lhd x= 0 \text{ implies } \lhd x =0 \\
 \intertext{and}
 \lhd \lcd x = 0 \text{ implies } \lcd x = 0
\end{gather*}
for all $x\in V$. In other words, $\lhd$ and $\lcd$ are disjoint if and only if
\begin{equation}\label{eq:disjointness}
 \ker \lcd \cap \im \lhd = 0 \quad \& \quad \ker \lhd \cap \im \lcd = 0.
\end{equation}

%TODO Co zkusit pozadovat, aby $V=\im\lhd \oplus \ker \lcd$ a vice versa?

The \emph{laplacian} is then defined as
\[\lap = \lcd \lhd + \lhd \lcd.\] We note that $\lap  = (\lhd + \lcd)^2$ and hence one can consider $\lhd + \lcd$ as the Dirac operator for the laplacian $\lap$. %See the book \cite{huang} for investigations of this Dirac operator.

\begin{proposition}%[Proposition 2.1 of \cite{kostant_lie_1961}]
 Let the notation be as above and assume $\lcd$ and $\lhd$ are disjoint and $\dim V < \infty$. Then
 \begin{equation}\label{eq:hodge_decomp_aux}
  \ker \lap = \ker \lcd \cap \ker\lhd \quad \& \quad  \im \lap = \im \lhd \oplus \im \lcd.
 \end{equation}
 Also one has a direct sum decomposition (\emph{Hodge decomposition}),
 \begin{equation}\label{eq:hodge_decomp}
    V = \im \lcd \oplus \ker \lap \oplus \im \lhd.
 \end{equation}
\end{proposition}
\begin{proof}
To prove the first equality of \eqref{eq:hodge_decomp_aux} we just use the definition of disjointness \eqref{eq:disjointness} of $\lhd$ and $\lcd$. The inclusion $\ker \lhd \cap \ker \lcd \subseteq \ker\lap$ is trivial. Let $x \in \ker \lap$ and put $y=-\lhd\lcd x$. Then $\lhd y =0$ and also $y =\lcd\lhd x$. Thus $\lhd\lcd\lhd x = 0$ and by disjointness this implies that $\lcd\lhd x = 0$ which, for the same reason, implies $\lhd x = 0$. Similarly $\lcd x = 0$. The remaining two decompositions of \eqref{eq:hodge_decomp_aux} are direct consequence of $\ker\lap = \ker\lhd\cap\ker\lcd$ and of disjointness of $\lhd$ and $\lcd$.

 It is obvious that $\im \lap \subseteq \im \lcd + \im \lhd$ and  by \eqref{eq:hodge_decomp_aux} and disjointness \eqref{eq:disjointness} we have $(\im \lhd + \im \lcd) \cap \ker \lap = 0$. If follows that $\im \lap \cap \ker \lap =0$. Since $V$ is finite-dimensional, we get $\dim \ker\lap + \dim \im \lap = \dim V$ and \eqref{eq:hodge_decomp}  and the second equality of \eqref{eq:hodge_decomp_aux} follows.
\end{proof}

\begin{corollary}
 Under the assumptions of the previous proposition, there are decompositions
  \begin{equation}
    \quad \ker \lhd = \im \lhd \oplus \ker \lap, \quad \ker \lcd = \im\lcd\oplus\ker\lap.
  \end{equation}
  Consequently we have isomorphisms
  \begin{equation}\label{eq:kerlap_iso}
    \ker \lap \simeq \ker \lcd /\im \lcd \quad\&\quad \ker \lap \simeq \ker \lhd / \im \lhd
  \end{equation}
  given by restriction to $\ker \lap$ of the canonical mappings $\ker \lcd \to \ker \lcd / \im \lcd$ and $\ker \lhd \to \ker \lhd / \im \lhd$.
\end{corollary}
\begin{proof}
 This is a direct consequence of the Hodge decomposition \eqref{eq:hodge_decomp}.
\end{proof}

\begin{remark}
 For any two linear mappings $\lhd$ and $\lcd$ on a vector space $V$ such that $\im\lhd\cap\im\lcd = 0$ we have that \[ \ker (\lhd + \lcd)  = \ker \lhd \cap \ker \lcd.\] Under our assumptions we get that $\ker (\lhd +\lcd) = \ker \lap$, since $\im \lhd \subseteq \ker \lhd$ and by disjointness \eqref{eq:disjointness} $\im \lhd \cap \im \lcd = 0$.
\end{remark}


For better understanding of how our operators act we represent them in a block matrix form with respect to the Hodge decomposition \eqref{eq:hodge_decomp}
\[
 \lcd = \begin{pmatrix} 0 & 0 & A\\0&0&0\\0&0&0\end{pmatrix} \quad \lhd = \begin{pmatrix} 0 & 0 &0\\0&0&0\\ B&0&0\end{pmatrix} \quad
 \lap = \begin{pmatrix}
	  AB & 0 & 0 \\
	  0 & 0 & 0 \\
	  0 & 0 & BA
	\end{pmatrix},
\]
where $A$ is the restriction of $\lcd$ to $\im\lhd$ and $B$ is the restriction of $\lhd$ to $\im \lcd$.

There is a convenient way to construct pairs of disjoint operators.
\begin{proposition} %TODO jak je to s im adjungovaneho operatoru? v konecne dimenzi by ta podminka na nedegenerovanost na im adjunktu mela byt nadbytecna. v nekonecne?
 Let $\lhd$ be a differential on a vector space $V$ endowed with a non-degenerate bilinear (respectively sesquilinear) form $\langle \, , \, \rangle$ and let $\lcd$ be the adjoint of $\lhd$ with respect to $\langle \, , \, \rangle$. If the restriction of $\langle \, , \, \rangle$ to $\im \lhd$ and $\im \lcd$ are non-degenerate, then $\lhd$ and $\lcd$ are disjoint and the Hodge decomposition \eqref{eq:hodge_decomp} is orthogonal with respect to $\langle \, , \, \rangle$.
\end{proposition}
\begin{proof}
 It is trivial to see that $\lcd$ is a differential, for we have 
 \[ 0 = \langle \lhd ^2 x, y \rangle = \langle x, \lcd^2 y \rangle\]
 for all $x,y\in V$.

 To prove \eqref{eq:disjointness}, let $x\in V$ be such that $\lhd \lcd x = 0$. We get
 \[ 0 = \langle \lhd\lcd x , y \rangle = \langle \lcd x, \lcd y \rangle \]
 for all $y\in V$. By our assumptions is the bilinear (resp. sesquilinear) map $(x,y) \to \langle \lcd x, \lcd y \rangle$ non-degenerate and hence we conclude that $\lcd x = 0$. Exchanging the roles of $\lhd$ and $\lcd$ in this computation we get that also $\lcd \lhd x =0$ implies $\lhd x=0$.

 Orthogonality of the Hodge resolution follows from $\ker \lhd = (\im\lcd)^\perp$ and $\ker \lcd = (\im \lhd)^\perp$.
\end{proof}
\begin{corollary}
 Let $V$ be endowed with a scalar product $\langle \, , \, \rangle$ and a differential $\lhd$. Let $\lcd$ be the adjoint of $\lhd$. Then $\lhd$ and $\lcd$ are disjoint operators. 
\end{corollary}
\begin{proof}
 This is trivial as the restriction of $\langle \, , \, \rangle$ to any subspace is non-degenerate.
\end{proof}

 If $V$ is infinite-dimensional and $L$ is any closed subspace of finite codimension, then any algebraic complementary subspace to $L$ in $V$ is also a topological complement (\cite{schaefer}). We further impose on $\lhd$ and $\lcd$ that the are continuous with closed image\footnote{We note that for a finite-dimensional vector space $V$ are these topological conditions automatically satisfied for all linear operators.}


%\subsection{Hodge decompositions and Kostant's theorem}
%TODO konecne rozmerny pripad

\begin{definition}
A real parabolic subalgebra (of some real form of $\lie{g}$, possibly different from $\lie{g}_0$) $\lie{q}_0$ is  \emph{admissible}, if it's complexification $\lie{q}$ is  $\theta$-stable,\footnote{Parabolic subalgebra $\lie{q}$ is $\theta$-stable iff $\lie{q}\cap\overline{\lie{q}}=\lie{l}$ and $\theta \lie{q}=\lie{q}$.} where $\theta$ is the Cartan involution associated to the real form $\lie{g}_0$ and for $\lie{q}=\lie{l}\oplus\lie{u}_+$ it holds that $\lie{l}\subseteq \lie{k}$ and $\lie{p}_+\subseteq\lie{u}_+$.
\end{definition}

The authors of \cite{huang_dirac_2006} proved that if $\rep{V}$ is a unitarizable $(\lie{g},K)$-module and $\lie{u}_+$ is the nilradical of an admissible real Lie algebra, then the Hodge decomposition of $C_\bullet(\lie{u}_+,\rep{V})$ is still valid. We compute several explicit examples in the next chapter. %TODO pridat odkaz na kapitolu

The article \cite{boe_kostant_2009} provides classification of simple modules in certain parabolic BGG categories $\mathcal{O}_S$. The classification is given by subdiagrams of the Dynkin diagram. The proof of Theorem \ref{thm:cohomology} is based on an equivalence of categories given in \cite{enright_categories_1987}. This equivalences relate the relevant blocks in $\mathcal{O}_S$ to blocks for a lower rank algebras. In this way the unitarizable highest weight modules correspond to finite-dimensional ones for which the Kostant formula is known. It also follows that the structure of the resolutions is preserved. The Table \ref{tbl:sing}, taken from \cite{boe_kostant_2009}, shows the relevant information. 

Let $J$ denote the set of singular simple roots, i.e. \[J= \{ \alpha \in \roots^0 | (\lambda+\rho,\check{\alpha}) = 0 \}.\] The columns $\alpha$ and $\alpha'$ give the crossed roots in the Dynkin diagrams. Each Kostant module\footnote{These are the modules $M$ in $\mathcal{O}$ for which there's is a combinatorial formula for $H^i(\lie{p}_-,M)$ of certain type. The unitarizable highest weight modules are Kostant modules according to \cite{davidson_differential_1991}. For details see \cite{boe_kostant_2009}.} corresponds to a connected subdiagram of $\mathcal{D}'$ containing $\alpha'$. Each such subdiagram gives a parabolic pair and the Kostant modules correspond to finite-dimensional modules for the semisimple part of the Levi factor of $\mathcal{D}'$.

\begin{table}[h] 
%\begin{center}
\begin{tabular}{cccccc}
$\mathcal{D}$ &  $\alpha$ & $|J|$ & $\mathcal{D}'$ & $\alpha'$    \\[2pt] \hline 
$(A_n,A_{r-1}\times A_{n-r})$ & $\a_r$   & $t$ & $(A_{n-2t},A_{r-t-1}\times A_{n-r-t})$ & $\a_{r-t}$ \\
$(B_n,B_{n-1})$ & $\alpha_1$   & 1 (short) & $\varnothing$  & --  \\
$(B_n,B_{n-1})$ & $\a_1$   & 1 (long) & $\varnothing$ & --  \\
$(C_n,A_{n-1})$ & $\a_n$   & $t$ (all short) & $(D_{n+1-2t},A_{n-2t})$  & $\a_{n+1-2t}$  \\
$(C_n,A_{n-1})$ & $\a_n$   & $t$ (1 long) & $(D_{n+1-2t},A_{n-2t})$  & $\a_{n+1-2t}$ \\
$(D_n,D_{n-1})$ & $\a_1$   & 1 & $(A_1,\varnothing)$  & $\a_1$  \\
$(D_n,D_{n-1})$ & $\a_1$   & 2 ($\{n-1,n\}$) & $\varnothing$  & --   \\
$(D_n,A_{n-1})$ & $\a_n$   & $t$ & $(D_{n-2t},A_{n-2t-1})$  & $\a_{n-2t}$  \\
$(E_6,D_5)$ & $\a_6$   & 1 & $(A_5,A_4)$  & $\a_5$ \\
$(E_6,D_5)$ & $\a_6$   & 2 & $\varnothing$  & --  \\
$(E_7,E_6)$ & $\a_7$   & 1 & $(D_6,D_5)$  & $\a_1$   \\
$(E_7,E_6)$ & $\a_7$   & 2 & $(A_1,\varnothing)$  & $\a_1$  \\
$(E_7,E_6)$ & $\a_7$   & 3 ($\{2,5,7\}$) & $\varnothing$  & --   \\[2pt] \hline
\end{tabular}
\medskip
\caption{Data for singular Hermitian symmetric categories}\label{tbl:sing}
%\end{center}
\end{table}

