\chapter{Unitarizable highest weight modules}

The class of unitarizable highest weight modules was classified in the eighties independently by \cite{jakobsen_hermitian_1983}, \cite{zuckermann} and \cite{enright_classification_1983}. The proof of the classification result was later improved in \cite{joseph_annihilators_1992}. In this section we follow mainly the article  \cite{enright_classification_1983}.

\section{Classification}

The algebra $\lie{k}$ has a one-dimensional center which is complementary to the span of $\roots_c$. We pick a generator $\zeta$ of the center by requiring $\frac{2 \langle \zeta,\beta \rangle}{\langle \beta, \beta \rangle} = 1$, where $\beta$ is the unique maximal noncompact root\footnote{Equivalently, $\beta$ is the highest weight of $\lie{k}$-representation $\lie{p}_+$.} of $\roots^+$. Now any line $\lambda+z\zeta$ for $z\in\C$ can be uniquely written as $\lambda_0 + z\zeta$ with
\[
 \langle \lambda_0 + \rho,\beta \rangle = 0, \quad \rho =\sum_{\alpha\in\roots^+} \alpha.
\]

If $L(\lambda)$ is an irreducible unitarizable module for $\lambda=\lambda_0+z\zeta$, then $z$ must be real and the $K_\C$-finiteness implies that $\lambda$ must be $\roots^+_c$-dominant integral. Write the generalized Verma module $M(\lambda)$ as $S(\lie{p}_+)\otimes F(\lambda_0) \otimes \C_z\zeta$. If we fix a basis of $\lie{g}$ and $F(\lambda_0)$, we may view the modules $M(\lambda)$ as defined on the same vector space $S(\lie{p}_+)\otimes F(\lambda_0)$ where the action of $\lie{g}$ is given by polynomial expressions in $z$. Likewise, we may view the Shapovalov form on $M(\lambda)$ as a bilinear form on $S(\lie{p}_+\otimes F(\lambda_0)$ with values in complex polynomials $\C[z]$.

A $\lie{g}$-module $M$ is called unitarizable if there exists (necesarilly unique up to a multiple) positive definite contravariant form on $M$. The preceding paragraph explains the structure of the set of $z\in\R$ such that the module $M(\lambda)$ is unitarizable.

\begin{figure}[H]\label{fig:struct}
  \begin{center}
  \begin{tikzpicture}
      \node[croot] at (2,0) [label=above:$A(\lambda_0)$] {};
      \node[croot] at (3,0) {};
      \node[croot] at (6,0) [label=above:$B(\lambda_0)$] {};
      \draw[thick] (0,0) to (2,0);
      \draw [dotted] (4,0) to (5,0);
      \draw[<->] (2,-0.5) -- (3,-0.5);
      \node at (2.5,-0.5) [label=below:$C$] {};
  \end{tikzpicture}
  \end{center}\caption{Structure of unitarizable weights} %TODO dodelat mark na 0
\end{figure}

\begin{theorem}[Theorem 2.4 of \cite{enright_classification_1983}]
 The set of real numbers $z$ with $L(\lambda_0 + z\zeta)$ a unitarizable $\lie{g}$-module is given by the set
\[
  \{z \in \mathbb{R}\, |\, z \leq A(\lambda_0)\} \cup \{ z=A(\lambda_0) + k C(\lambda_0)\,|\, z \leq B(\lambda_0) \et k\in \mathbb{N}_0\},
\]
where $A(\lambda_0)$, $B(\lambda_0)$ and $C(\lambda_0)$ are real numbers expressible in terms of certain root systems $Q(\lambda_0)$ and $R(\lambda_0)$ associated to $\lambda_0$. Moreover $C(\lambda_0)$ is independent of $\lambda_0$ and depends only on the type of $\lie{g}_0$. The values of $C$ are listed in Table \ref{tbl:C} and the structure of the set of unitarizable highest weights is depicted in Figure \ref{fig:struct}.
	
The discrete series representation corresponds to $z <0$ and limit of discrete series representation corresponds to $z=0$. For $z  < A(\lambda_0)$ we have $L(\lambda) = M(\lambda)$ (i.e. the generalized Verma modules are irreducible) and for all $z \geq A(\lambda_0)$ such that $L(\lambda)$ are unitarizable the generalized Verma modules are reducible.%, hence the elements of  $\{z=A(\lambda_0) + kC| \, z \leq B(\lambda_0) \et k\in \mathbb{N}_0 \}$ are called  reduction points or points of reducibility.

\begin{table}[h]\label{tbl:C}
\[\begin{array}{c|ccccccc}
\lie{g}_0 & \mathrm{SU}(p,q) & \mathrm{Sp}(n,\mathbb{R}) & \mathrm{SO}^*(2n) & \mathrm{SO}(2,2n-2) & \mathrm{SO}(2,2n-1) & \mathrm{E}_6 & \mathrm{E}_7\\\hline
C & 1 & \frac{1}{2} & 2 & n-2 & n-\frac{3}{2} & 3 & 4
\end{array}\]\caption{Distance between points of reducibility}
\end{table}
\end{theorem}

Let $\roots_c(\lambda_0) := \{ \alpha \in \roots_c | \langle \alpha,\lambda_0 \rangle = 0 \}$ and recall the definition of $\beta$ the maximal non-compact root. Take the root subsystem of $\roots$ generated by $\pm \beta$ and $\roots_c(\lambda_0)$ and decompose it into a disjoint union of simple root systems. Let $Q(\lambda_0)$ be the root system in this union which contains $\beta$.

If $\roots$ has two root lengths and if there are short compact roots $\alpha$ not orthogonal to $Q(\lambda_0)$ with $\frac{2 \langle \lambda_0,\alpha \rangle}{\langle \alpha, \alpha \rangle}  =1$, then let $\Psi$ be the root system generated by $\pm \beta, \roots_c(\lambda_0)$ and all such $\alpha$. Let $R(\lambda_0)$ be the simple component of $\Psi$ which contains $\beta$. If $\roots$ has only one root lenght or if no such $\alpha$ exists, then put $R(\lambda_0) = Q(\lambda_0)$.

Since these root systems are subsystems of $\roots$ and since each has compact and noncompact roots, each is a root system of a Hermitian symmetric pair.

There is a convenient way to construct $Q(\lambda_0)$ by means of Dynkin diagrams. Draw a Dynkin diagram of $\lie{g}$ and delete the unique node corresponding to simple noncompact root. Now adjoin to the resulting diagram $-\beta$ by the usual rules as when constructing extended Dynkin diagrams. The maximal connected subdiagram containing $-\beta$ such that its every compact simple root is orthogonal to $\lambda_0$ is the Dynkin diagram of $Q(\lambda_0)$. We illustrate on the case of $\lie{su}(p,q)$. Here the noncompact root $\beta$ is $\alpha_p$ and we get the following extended Dynkin diagram.
\begin{figure}[H]\label{fig:Q}
  \begin{center}
     \begin{tikzpicture} % SU(p,q) ~ A_{n-1} relative
	\node[croot] (a1) [label=below:$\alpha_1$] {};
	\node[croot] (a2) [right= of a1] [label=below:$\alpha_2$] {};
	\node[croot] (a3) [right= of a2] [label=below:$\alpha_3$] {};
	\node (a4) [right= of a3] {};
	\node[nroot] (a5) [above right=of a4] [label=above:$-\beta$] {};
	\node (a6) [below right=of a5] {};
	\node[croot] (a7) [right=of a6] [label=below:$\alpha_{n-3}$] {};
	\node[croot] (a8) [right=of a7] [label=below:$\alpha_{n-2}$] {};
	\node[croot] (a9) [right=of a8] [label=below:$\alpha_{n-1}$] {};
	\draw (a1) to (a2) to (a3); \draw [dotted] (a3) to (a4);
	\draw [dotted](a6) to (a7);
	\draw (a7) to (a8) to (a9);
	\draw (a1) to (a5) to (a9);
     \end{tikzpicture}
  \end{center}\caption{The Dynkin diagram of $Q(\lambda_0)$} 
\end{figure}
If we write with respect to the basis of fundamental weights $\lambda_0 = \sum_i a_i \omega_i$ we see that $Q(\lambda_0)$ is a root system of $\lie{su}(p',q')$ where $p'$ and $q'$ are maximal such that the coefficients $a_1,a_2,\ldots,a_{p'}$ and $a_{n-q'+1},a_{n-q'+2}, \ldots, a_n$ are nonzero.

The root system $R(\lambda_0)$ is different from $Q(\lambda_0)$ only in two cases. The first one is $\lie{g}_0=\lie{sp}(n,\R)$ where $Q(\lambda_0) = \lie{sp}(n',\R)$ and $R(\lambda_0) = \lie{sp}(n'',\R)$ with $n' < n'' \leq n$. The second one is $\lie{g}_0=\lie{so}(2,2n-1)$ where $Q(\lambda_0) = \lie{su}(1,n-1)$ and $R(\lambda_0) = \lie{so}(2,2n-1)$ with $\lambda_0 = (\lambda_1,\frac{1}{2},\ldots,\frac{1}{2})$ in the $\epsilon$-basis.

The following two theorems finish the general classification of unitarizable highest weight modules.

\begin{theorem}[Theorem 2.8 of \cite{enright_classification_1983}]
 Let $\roots^+_{c,1} := \roots^+_c \cap Q(\lambda_0)$ and let $\roots^+_{c,2} := \roots^+_c \cap R(\lambda_0)$. Denote by $\rho_{c,i}$ half of the sum of roots in $\roots^+_{c,i}$.
 
 If $\lie{g}_0=\lie{so}(2,2n-1)$ and $Q(\lambda_0) \neq R(\lambda_0)$ then \[B(\lambda_0) = 1 + \frac{\langle \rho_{c,2},\beta\rangle}{\langle \beta, \beta \rangle}.\]
 In all other cases \[B(\lambda_0) = 1 + \frac{ \langle \rho_{c,1} + \rho_{c,2} , \beta \rangle}{\langle \beta, \beta \rangle}.\]
\end{theorem}


\begin{theorem}[Theorem 2.10 of \cite{enright_classification_1983}]\label{thm:reduction_points}
 The first reduction point $A(\lambda_0)$ is given by\footnote{Or in other words: The number of reduction points equals the split rank of $Q(\lambda_0)$.}
 \[
   A(\lambda_0) = B(\lambda_0) - (\text{split rank } Q(\lambda_0) -1) C.
 \]
\end{theorem}

Now let's see what we can tell about the maximal module $J(\lambda)$ of the generalized Verma module $M(\lambda)$. %The following was proved in \cite{davidson_differential_1991}.

\begin{theorem}[Theorem 3.1 of \cite{davidson_differential_1991}]
 Suppose $L(\lambda) = M(\lambda)/J(\lambda)$ is unitarizable and $J(\lambda)\neq 0$. Then
 \begin{enumerate}
  \item $H^1(\lie{p}_-,L(\lambda))$ is an irreducible $\lie{k}$-module
  \item $J(\lambda)$ is generated over $S(\lie{p}_+)$ by an irreducible $\lie{k}$-submodule $J(\lambda)^0$ isomorphic to $H^1(\lie{p}_-,L(\lambda))$.
 \end{enumerate}
\end{theorem}


%Let $J(\lambda)$ denote the maximal submodule of the generalized Verma module $M(\lambda)$. For all unitarizable highest weight modules we have  $J(\lambda)$  generated by $\lie{U(g)}$ from an irreducible $\lie{k}$-module.
In particular, the generator of $J(\lambda)$ must be contained in some component $S^k(\lie{p}_+)\otimes F(\lambda)$. This $k$ is called \emph{level of reduction} of $L(\lambda)$ and is denoted by $l(\lambda)$.

\begin{definition}
 The set of reduction points $\Lambda_r$ is the union of all reduction points. Explicitly
 \[
 \Lambda_r := \{ \lambda = z\zeta + \lambda_0 \in \lie{h}^* | z = A(\lambda_0) +kC, k\in\N_0, z \leq B(\lambda_0) \}.
 \]

 For $\lambda \in \Lambda_r$ let $a(\lambda) := (Q(\lambda_0),R(\lambda_0),l(\lambda))$ and let $\mathcal{A}$ denote the set of all such triples as $\lambda$ ranges over $\Lambda_r$. For $a\in\mathcal{A}$, let $\Lambda_a$ denote the set of all $\lambda\in\Lambda_r$ with $a(\lambda)=a$.
\end{definition}

Now we can look more closely at the structure of the set of reduction points. 

\begin{corollary}[of \ref{thm:reduction_points}]
 Let $a=(Q,R,l)\in\mathcal{A}$ and let $\lambda\in\Lambda_a$. If we write $\lambda= z\zeta + \lambda_0$, then $z=B(\lambda)-(l-1)C$ and on the other hand for $\lambda=(B - nC)\zeta + \lambda_0 \in \Lambda_r$ we have $l(\lambda) =n+1$.
\end{corollary}

Let $\lie{h}^*_\R$ denote the real span of the roots. A \emph{cone} with vertex zero (in $\lie{h}^*_\R$) is the intersection of a (nonempty) collection of closed half spaces. Each cone $C$ is thus determined by a finite set $\{h_i \in \lie{h}|i=1,\ldots,k\}$ with $C= \{ \lambda \in \lie{h}^*_\R | \lambda(h_i) \geq 0, i=1,\ldots k\}$. An \emph{integral cone} will be the intersection of a cone with the set of all $\lie{k}$-integral points of $\lie{h}^*.$ For an integral element $\nu\in\lie{h}^*$, a translated cone with vertex $\nu$ is a set of the form $\nu + C$ with $C$ some integral cone.

\begin{definition}
 For $a=(Q,R,l)\in\mathcal{A}$, let $C_a$ be the integral cone of $\lie{k}$-dominant integral elements in $\lie{h}^*_\R$ which are orthogonal to elements in $R$.
\end{definition}

%Since the root system $R$ always contains $\beta$, the representations $L(\lambda)$ are in fact finite-dimensional for $\lambda\in C_a$.

For concrete calculations the following lemma can be useful. 

\begin{lemma}[Section 4.3 of \cite{enright_resolutions_2004}]
The cone $C_{Q, R, l}$ consists of positive integral multiples of weights of the form $\omega_i - (\omega_i, \beta^\vee) \zeta,$ where $\omega_i$ is a fundamental weight corresponding to simple root $\alpha_i$ that does not belong to $R$.
\end{lemma}
\begin{proof}
 Any  $\lie{k}$-dominant integral weight can be written in the form $\mu = \sum_i a_i \omega_i + b \zeta,$ where $a_i$ are nonnegative integers. Such a weight is perpendicular to $R$ if and only if it is perpendicular to all compact simple roots contained in $R$ and to the noncompact root $-\beta$, i.e. to the simple roots of the root system $R$. The crucial observation here is that for each Hermitian symmetric space the weight $\zeta$ is in fact the fundamental weight corresponding to the simple noncompact root. Hence we have 
\[
0 = \left(\sum a_i \omega_i + b \zeta, \alpha_i^\vee \right) = a_i 
\] 
for all compact simple roots of  $R$ and 
\[
0 = \left(\sum a_i \omega_i + b \zeta, \beta^\vee \right)
\]
for the noncompact root. Recalling the definition of $\zeta$ and solving for $b$ we see that the cone consists of vectors of the form $\sum a_i (\omega_i - (\omega_i, \alpha_i^\vee)\zeta)$ where the sum is only indices whose simple roots are not in $R$.
\end{proof}

\begin{proposition}[Proposition 6.6 of \cite{davidson_differential_1991}]
 The set of reduction points $\Lambda_r$ is the disjoint union of the sets $\Lambda_a, a\in\mathcal{A}$.

 Each set $\Lambda_a$ is a translated integral cone with vertex $\lambda_a + C_a$. We list the vertices $\lambda_a$ in the next section.
\end{proposition}
\begin{proof}
 The first statement is trivial and the second one follows by case by case computations.
\end{proof}

The next proposition gives an alternative way to compute the highest weight of the maximal submodule.

\begin{proposition}[Proposition 6.8 of \cite{davidson_differential_1991}]
 Suppose $\lambda\in\Lambda_a$ with $a=(Q,R,l)$. Let $u$ and $v$ denote respectively the unique elements of maximal length in the Weyl groups for the positive root systems $Q\cap \roots^+_c$ and $R\cap \roots^+_c$ and let $\mu$ denote the highest weight of the maximal submodule $J(\lambda)$. Then
 \[
  \mu = \lambda + \frac{1}{2}(u \mu_l + v \mu_l)
 \]
 in all cases except when $\lie{g}_0=\lie{so}(2,2n-1)$ and $Q\neq R$. In this case
 \[
  \mu = \lambda + \frac{1}{2}(\mu_l + v\mu_l).
 \]

 Moreover, in all cases $F(\mu)$ occurs with multiplicity one in $M(\lambda+\rho)$ and in all cases $F(\mu)$ is a PRV component of a tensor product in $S(\lie{p}_+)\otimes F(\lambda)$.
\end{proposition}

The next theorem  deals with effect of a sort of `translation functor' on unitarizable highest weight modules.
\begin{theorem}[Factorization theorem 6.15 of \cite{davidson_differential_1991}]
 Fix $a\in\mathcal{A}$ and let $\lambda = \lambda_a + \lambda'\in\Lambda_a$. Let $J(\lambda)^0$ and $J(\lambda_a)^0$ be the $\lie{k}$-modules that generate $J(\lambda)$ and $J(\lambda_a)$. Extend the $\lie{k}$-equivariant projection \[P:F(\lambda_a)\otimes F(\lambda') \to F(\lambda)\] to a mapping $\widetilde{P}:M(\lambda_a) \otimes F(\lambda') \to M(\lambda)$ by \[\widetilde{P}(F\otimes v) (T) := P(F(T)\otimes v),\]
  where we have used that $M(\lambda_a) = S(\lie{p}_+)\otimes F(\lambda_a)$.

Let $\mu$ and $\mu_a$ denote the highest weights of  $J(\lambda)^0$ and $J(\lambda_a)^0$. Then
 \begin{enumerate}
  \item $\mu  = \mu_a+\lambda'$
  \item $P(J(\lambda_a)^0\otimes F(\lambda')) = J(\lambda)^0$ and 
  \item $P(J(\lambda_a)\otimes F(\lambda')) = J(\lambda)$.
 \end{enumerate}
\end{theorem}

\section{Nilpotent cohomology of unitarizable highest weight modules}

The convention employed in this section is that we omit the terms whose indices are outside natural boundaries. 

\begin{definition}\label{def:cohomology_roots}
Let $\Psi_\lambda$ be the set if roots in $\roots$ which are orthogonal to $\lambda+\rho$ and let $\Psi_\lambda^+ = \Psi_\lambda \cap \roots^+$. Denote by $\roots_{n,\lambda}^+$ the roots which satisfy the following condititions
 \begin{enumerate}
    \item $\alpha \in \roots_n^+$ and $(\lambda+\rho,\alpha^\vee)$ is a positive integer;
    \item $\alpha$ is orthogonal to $\Psi_\lambda$;
    \item $\alpha$ is short if there exist a long root in $\Psi_\lambda$.
 \end{enumerate}
 
 Let $W_\lambda$ be the subgroup of $W$ which is generated by reflections $s_\alpha$ for $\alpha\in \roots_{n,\lambda}^+$.
 
 Let $\roots_\lambda$ be the subset of $\roots$ of elements $\beta$ with $s_\beta\in W_\lambda$ and let $\roots_{\lambda,c} = \roots_c \cap \roots_\lambda$, $\roots_{\lambda,c}^+ = \roots_{\lambda,c} \cap \roots^+$.
 
 Finally, define  $W^{c,i}_\lambda = \{ w \in W_\lambda | w \rho \text{ is } \roots^+_{\lambda, c}\text{-dominant and } l_\lambda(w)=i \}$.
\end{definition}


\begin{theorem}[3.7 \cite{davidson_differential_1991}]\label{thm:cohomology}
 Let $L$ be unitarizable with highest weight $\lambda $. Then for $i\in \mathbb{N}$ we have
\[
 H^i(\lie{p}_+,L)\simeq \bigoplus_{w\in W^{c,i}_\lambda} F(\overline{w(\lambda+\rho)} - \rho)
\]
where  $\overline{\lambda}$ is the unique $\roots_c^+$-dominant element in the $W_c$ orbit of $\lambda$.
\end{theorem}

\begin{remark}
 The $\lie{k}$-weight of the first cohomology is given by $\lambda_0-\rho$ where $\lambda_0$ is the unique $\roots_c^+$ dominant element in the $W_c$ orbit of $s_{\gamma_0}\lambda$ for the unique noncompact simple root $\gamma_0 \in \roots_\lambda^+$.
\end{remark}

\begin{lemma}\label{lem:singular_are_noncompact}
 Let $\lambda$ be a highest weight of a unitarizable highest weight module. If a positive root is orthogonal to $\lambda + \rho$ then it must be noncompact.
 \[
  \alpha \in \roots^+: \alpha \perp \lambda + \rho \Longrightarrow \alpha \in \roots^+_n
 \]
\end{lemma}
\begin{proof}
 Every positive roots can be written as a positive linear combination of simple roots, i.e. $\alpha = \sum_i c_i \alpha_i$ where $c_i \geq 0$. The fundamental weights form a basis of $\lie{h}^*$ and thus $\lambda = \sum_i k_i \omega_i$. Now we just use the defining property of fundamental weights $\frac{2(\alpha_i,\omega_j)}{(\alpha_i,\alpha_i)} = \delta_{ij}$ to compute
 \begin{align*}
  (\alpha,\lambda+\rho) & = \sum_{i,j} \left(  c_i k_j (\alpha_i,\omega_j) + c_i (\alpha_i,\omega_j) \right ) \\
			& = \sum_{i,j} \left( c_i k_j \frac{(\alpha_i,\alpha_i)}{2} \delta_{ij} + c_i \frac{(\alpha_i,\alpha_i)}{2} \delta_{ij} \right ) \\
			& = \sum_i c_i \frac{(\alpha_i,\alpha_i)}{2} (k_i + 1).
 \end{align*}
 If $\lambda$ is a highest weight of a unitarizable module, then all but one of the coefficients $k_i$ are nonnegative and the only possibly negative coefficient corresponds to the fundamental weight dual to the coroot of the unique noncompact simple root - let's denote it's index by $i_0$. If the scalar product $(\alpha, \lambda+\rho)$ is zero, then $c_{i_0}$ must be nonzero -- all the remaining terms in the sum are nonnegative. But $c_{i_0} \neq 0$ is equivalent to $\alpha$ being noncompact.
\end{proof}


There is a fair amount of work which builds on top of these results. It was proven (\cite{enright_hilbert_2004,boe_kostant_2009}) that the formula for Lie algebra cohomology is equivalent for the module to have a BGG-like resolution in terms of Verma modules. These resolutions are explicitely computed for the two expceptional types in \cite{enright_resolutions_2004}. The paper \cite{enright_hilbert_2004} treats also the classical types $\lie{su}(p,q)$, $\lie{sp}(n,\R)$ and $\lie{so}^*(2n)$ to some degree. So what remains to be done are the orthogonal cases $\lie{so}(2,2p)$. 

\begin{example} 
 Let us take $\lie{g} = \lie{so}(2,2n-2)$ with $\lambda = (2-n)\omega_1$. Then in the epsilon basis we have $\lambda + \rho = (1,n-2,\ldots,1,0)$ and $\Psi_\lambda^+ = \{ \epsilon_1 - \epsilon_{n-1}\}$. The only noncompact root that is orthogonal to $\epsilon_1 -  \epsilon_{n-1}$ and whose scalar product with $\lambda + \rho$ is positive integral is $\alpha = \epsilon_1 + \epsilon_{n-1}$. Thus we get $\roots_{n,\lambda}^+ = \epsilon_1 + \epsilon_{n-1} = \roots_\lambda$. It follows that
\begin{align*}
 H^0(\lie{p}_-,L((2-n)\omega_1)) &= F((2-n)\omega_1)\\
 H^1(\lie{p}_-,L((2-n)\omega_1)) &= F(-n\omega_1)\\
 H^i(\lie{p}_-,L((2-n)\omega_1)) &= 0 \text{ for } i\geq 2.
\end{align*} 

Similarly there is only one root generating $W_\lambda$ for $\lie{g} = \lie{so}(2,2n-1)$ and $\lambda = (\frac{3}{2} - n)\omega_1$ and we get that in that case
\begin{align*}
 H^0(\lie{p}_-,L((\frac{3}{2}-n)\omega_1)) &= F((\frac{3}{2}-n)\omega_1)\\
 H^1(\lie{p}_-,L((\frac{3}{2}-n)\omega_1)) &= F((-\frac{1}{2}-n)\omega_1)\\
 H^i(\lie{p}_-,L((\frac{3}{2}-n)\omega_1)) &= 0 \text{ for } i\geq 2.
\end{align*}

Moreover, by inspecting the tables \ref{tbl:so_even} and \ref{tbl:so_odd}, we see that in both of these cases the cone $C_a$ is empty.
\end{example}


\clearpage
\input{cohomology_sl}
\clearpage
\input{cohomology_sp} 
\clearpage
\input{cohomology_so}
\clearpage
\input{cohomology_conformal_even}
\clearpage
\input{cohomology_conformal_odd}
\clearpage
\subsection[Exceptional cases]{Exceptional cases}

\subsubsection{$\mathrm{E_6}$}

\begin{center}
    \begin{tikzpicture}% E6 relative
        \node[nroot] (a1) [label=above:$\alpha_1$] {};
        \node[croot] (a3) [right=of a1] [label=above:$\alpha_3$] {};
        \node[croot] (a4) [right=of a3] [label=above:$\alpha_4$] {};
        \node[croot] (a5) [right=of a4] [label=above:$\alpha_5$] {};
        \node[croot] (a6) [right=of a5] [label=above:$\alpha_6$] {};
        \node[croot] (a2) [below=of a4] [label=right:$\alpha_2$] {};
        \draw (a1) to (a3) to (a4) to (a5) to (a6);
        \draw (a4) to (a2);
     \end{tikzpicture}
\end{center}
%
%\[\alpha_2 = \epsilon_1+\epsilon_2,\quad \alpha_i = \epsilon_{i-1}-\epsilon_{i-2},\quad (3\leq i \leq 6)\]
%\[\alpha_1 = \frac{1}{2}(\epsilon_1-\epsilon_2-\epsilon_3- \cdots -\epsilon_6 -\epsilon_7 + \epsilon_8)\]
%
%\[\roots_c^+ = \{ \pm\epsilon_i + \epsilon_j | 1\leq i < j \leq  5\}\]
%\[\roots_n^+ = \left\{  \frac{1}{2}\sum_{i=1}^5 (-1)^{\nu(i)}\epsilon_i - \epsilon_5 -\epsilon_7 + \epsilon_8\, |\, \sum_{i=1}^5 \nu(i)\text{ is even} \right \} \]
%\[\beta = \frac{1}{2}(\epsilon_1+\epsilon_2+\epsilon_3+\epsilon_4+\epsilon_5-\epsilon_6-\epsilon_7+\epsilon_8) =\alpha_1+2\alpha_2+2\alpha_3+3\alpha_4+2\alpha_5+\alpha_6\]
%\[\quad \rho = (0,1,2,3,4,-4,-4,4),\quad \zeta = (0,0,0,0,0,\frac{-2}{3},\frac{-2}{3},\frac{2}{3})\]
 %
%\begin{figure}[H]
  %\centering
  %\input{diagrams/nroots_E6_1.tikz} 
  %\caption{Poset of noncompact roots for $\mathrm{E}_6$}
%\end{figure}  

% \begin{table}[h]
\begin{center}\begin{threeparttable}\label{tbl:e6}
\begin{tabular}{CCCCC}
  \text{Vertex } \lambda_a & \text{Weight } \mu_a & Q(\lambda_a) = R(\lambda_a) & l(\lambda_a) \\ \hline
  -12 \omega_1 + \omega_2 & -12 \omega_1 & \mathrm{SU}(1,1) & 1\\
  -12 \omega_1 + \omega_4 & -12 \omega_1 + \omega_2 & \mathrm{SU}(1,2)& 1\\
  -12 \omega_1 + \omega_3 + \omega_5 & -12 \omega_1 + \omega_4 & \mathrm{SU}(1,3) & 1\\
  -9 \omega_1 + \omega_5 \tnote{1} & -10 \omega_1 + \omega_3 & \mathrm{SU}(1,4) & 1\\
  -10 \omega_1 + \omega_3 + \omega_6 \tnote{2} & -10 \omega_1 + \omega_5 & \mathrm{SU}(1,4) & 1\\
  -8 \omega_1 + \omega_3 & -8 \omega_1+ \omega_6 & \mathrm{SU}(1,5) & 1 \\
  -5 \omega_1 +  \omega_6 & -6 \omega_1+ \omega_2 & \mathrm{SO}(2,8) & 1 \\
  -8 \omega_1 + \omega_6 & -9 \omega_1 & \mathrm{SO}(2,8) & 2 \\
  0 & -2 \omega_1+ \omega_3 & EIII & 1 \\
  -3 \omega_1 & -5 \omega_1 + \omega_6 & EIII & 2
\end{tabular}
\smallskip
\begin{tablenotes}
 \item [1] Dynkin diagram
    \begin{tikzpicture} % E6 relative
        \node[croot] (a1) [label=above:$-\beta$] {};
        \node[croot] (a2) [right=of a1] [label=above:$\alpha_2$] {};
        \node[croot] (a3) [right=of a2] [label=above:$\alpha_4$] {};
        \node[croot] (a4) [right=of a4] [label=above:$\alpha_3$] {};
	\draw (a1) to (a2) to (a3) to (a4);
     \end{tikzpicture}
 \item [2] Dynkin diagram
 \begin{tikzpicture} % E6 relative
        \node[croot] (a1) [label=above:$-\beta$] {};
        \node[croot] (a2) [right=of a1] [label=above:$\alpha_2$] {};
        \node[croot] (a3) [right=of a2] [label=above:$\alpha_4$] {};
        \node[croot] (a4) [right=of a3] [label=above:$\alpha_5$] {};
	\draw (a1) to (a2) to (a3) to (a4);
     \end{tikzpicture}
\end{tablenotes}\caption{Vertices and root systems for $\mathrm{E}_6$}
\end{threeparttable}\end{center}
% \end{table}

\subsubsection{$\mathrm{E_7}$}

\begin{center}
     \begin{tikzpicture} % E7 relative
        \node[croot] (a1) [label=above:$\alpha_1$] {};
        \node[croot] (a3) [right=of a1] [label=above:$\alpha_3$] {};
        \node[croot] (a4) [right=of a3] [label=above:$\alpha_4$] {};
        \node[croot] (a5) [right=of a4] [label=above:$\alpha_5$] {};
        \node[croot] (a6) [right=of a5] [label=above:$\alpha_6$] {};
        \node[nroot] (a7) [right=of a6] [label=above:$\alpha_7$] {};
        \node[croot] (a2) [below=of a4] [label=right:$\alpha_2$] {};
        \draw (a1) to (a3) to (a4) to (a5) to (a6) to (a7);
        \draw (a4) to (a2);
     \end{tikzpicture}
\end{center}

 %
%\begin{figure}[H]
  %\centering
  %\input{diagrams/nroots_E7_7.tikz} 
  %\caption{Poset of noncompact roots for $\mathrm{E}_7$}
%\end{figure}  

\begin{center}\begin{threeparttable}
\begin{tabular}{CCCCC}
  \text{Vertex } \lambda_a & \text{Weight } \mu_a & Q(\lambda_a) = R(\lambda_a) & l(\lambda_a) \\ \hline
  \omega_1 - 18 \omega_7 & -18 \omega_7 & \mathrm{SU}(1,1) & 1 \\
  \omega_3 - 18 \omega_7 & \omega_1 -18 \omega_7 & \mathrm{SU}(1,2) & 1 \\
  \omega_4 - 18 \omega_7 & \omega_3 -18 \omega_7 & \mathrm{SU}(1,3) & 1 \\
  \omega_2 + \omega_5 - 18 \omega_7 & \omega_4 - 18 \omega_7 & \mathrm{SU}(1,4) & 1 \\
  \omega_5 -15 \omega_7 \tnote{1} &  \omega_2 - 15\omega_7 & \mathrm{SU}(1,5) & 1 \\
  \omega_2 + \omega_6 - 16 \omega_7 \tnote{2} &  \omega_5 - 16 \omega_7 & \mathrm{SU}(1,5) & 1 \\
  \omega_2 - 13 \omega_7 &  \omega_6 - 14 \omega_7 & \mathrm{SU}(1,6) & 1 \\
  \omega_6 - 10 \omega_7 &  \omega_1 - 10 \omega_7 & \mathrm{SO}(2,10) & 1 \\
  \omega_6 - 14 \omega_7 & -14 \omega_7 & \mathrm{SO}(2,10) & 2 \\
  0 &  \omega_6 - 2 \omega_7 & EVII & 1 \\
  -4 \omega_7 &  \omega_1 - 6 \omega_7 & EVII & 2 \\
  -8 \omega_7 & -10 \omega_7 & EVII & 3
\end{tabular}
\smallskip
\begin{tablenotes}
 \item [1] Dynkin diagram
    \begin{tikzpicture} % E6 relative
        \node[croot] (a1) [label=above:$-\beta$] {};
        \node[croot] (a2) [right=of a1] [label=above:$\alpha_1$] {};
        \node[croot] (a3) [right=of a2] [label=above:$\alpha_3$] {};
        \node[croot] (a4) [right=of a3] [label=above:$\alpha_4$] {};
        \node[croot] (a5) [right=of a4] [label=above:$\alpha_2$] {};
	\draw (a1) to (a2) to (a3) to (a4) to (a5);
     \end{tikzpicture}
 \item [2] Dynkin diagram
 \begin{tikzpicture} % E6 relative
        \node[croot] (a1) [label=above:$-\beta$] {};
        \node[croot] (a2) [right=of a1] [label=above:$\alpha_1$] {};
        \node[croot] (a3) [right=of a2] [label=above:$\alpha_3$] {};
        \node[croot] (a4) [right=of a3] [label=above:$\alpha_4$] {};
        \node[croot] (a5) [right=of a4] [label=above:$\alpha_5$] {};
	\draw (a1) to (a2) to (a3) to (a4) to (a5);
     \end{tikzpicture}
\end{tablenotes}\caption{Vertices and root systems for $\mathrm{E}_7$}
\end{threeparttable}\end{center}
% \end{table}

